UK

### 2020-09-28 UK/UK areas.Rmd
clean up for journal submission

#uk_hexmap <- create_hexmap(
#  shp = uk,
#  sf_id = "pcon17nm",
#  hex_size = 0.12,
#  focal_points = uk_cities,
#  verbose = TRUE)

@@

ggsave(plot = ukhexmap, filename = "ukhexmap.png", device = "png", dpi = 300)

```

>>>>

uk_hexmap <- create_hexmap(
  shp = uk,
  sf_id = "pcon17nm",
  hex_size = 0.12,
  focal_points = uk_cities,
  verbose = TRUE)

@@

ggsave(plot = ukhexmap, filename = "ukhexmap.png", device = "png", dpi = 300)
```
